\section{Microsoft SDK}
\label{sec:microsoftsdk}

Microsoft Windows \gls{sdk}, and its predecessors Platform \gls{sdk}, and .NET Framework \gls{sdk}, are \glspl{sdk} from Microsoft that contain documentation, header files, libraries, samples and tools required to develop applications for Microsoft Windows and .NET Framework. Platform \gls{sdk} specializes in developing applications for Windows 2000, XP and Windows Server 2003. .NET Framework SDK is dedicated to developing applications for .NET Framework 1.1 and .NET Framework 2.0. Windows SDK is the successor of the two and supports developing applications for Windows XP and later, as well as .NET Framework 3.0 and later.

Windows \gls{sdk} allows the user to specify the components to be installed and where to install them. It integrates with Visual Studio, so that multiple copies of the components that both have are not installed; however, there are compatibility caveats if either of the two is not from the same era.[4][5] Information shown can be filtered by content, such as showing only new Windows Vista content, only .NET Framework content, or showing content for a specific language or technology.

Use the latest sensor and the Kinect for Windows \gls{sdk} 2.0 to create Windows apps that run on PCs and tablets. Be sure to select "Windows 8.1" as a supported target during application authoring to ensure that your application also runs on Windows 10. Kinect for Windows v2 apps will continue to work after an upgrade to Windows 10. As always, we recommend that that you test applications on new platforms as they are released.